Moisture absorption and drying alter nonadditive litter flammability in a mixed conifer forest

### 2020-05-25 ms/Magalhaes_Schwilk_litter_flam_moisture.tex
Fix caption

\begin{figure}
  \centering
  \includegraphics[width=16cm]{figs_tables/fig1_dry_effects_by_taxon.pdf}
  \caption{}
\end{figure}
%%\clearpage
\begin{figure}
  \captionsetup{labelformat=adja-page}
  \ContinuedFloat
\caption{Effects of litter drying on fuel moisture and flammability. A) Dry
  down curves for eight species. Lines show best-fit exponential decay curves
  fit to moisture content on a dry mass basis. B) Flame spread rate by time
  since wetting. Lines indicate best fit linear model fits by taxonomic group.
  Model ANOVA table in Table \ref{tab:spreadrate_anova} and coefficients in SI
  Table 6. C) Percent fuel consumed by time since wetting. Curves shown
  indicate best fit beta regression lines by taxonomic group. Model ANOVA table
  in Table \ref{tab:consume_anova} and coefficients in SI Table 7.
  D) Flame spread rate by moisture content (model fit $F = 61.15$, df = 9, 148,
  $P < 0.0001$). Model ANOVA table in Table \ref{tab:spreadrate_anova} and
  coefficients in SI Table 4. E) Percent fuel consumed by moisture content.
  Lines indicate best fit beta regression lines. Model deviance table in Table
  \ref{tab:consume_anova} and coefficients are in SI Table 5. For plots in left
  column, horizontal jitter (0.5 to 2 hr) was added to avoid overplotting. A
  lack of data at earlier time points for a taxon indicates no ignitions
  occurred at those time points.}
 \label{fig:drydown}
\end{figure}
%% \clearpage

>>>>

\begin{figure}
  \centering
  \includegraphics[width=16cm]{figs_tables/fig1_dry_effects_by_taxon.pdf}
  \caption{}
\end{figure}
%%\clearpage
\begin{figure}
  \captionsetup{labelformat=adja-page}
  \ContinuedFloat
  \caption{Effects of litter drying on fuel moisture and flammability. A) Dry
    down curves for eight species. Lines show best-fit exponential decay curves
    fit to moisture content on a dry mass basis. B) Flame spread rate by time
    since wetting. Lines indicate best fit linear model by taxonomic group.
    Model ANOVA table in Table \ref{tab:spreadrate_anova} and coefficients in
    SI Table 6. C) Percent fuel consumed by time since wetting. Curves indicate
    best fit beta regression lines by taxonomic group. Model ANOVA table in
    Table \ref{tab:consume_anova} and coefficients in SI Table 7. D) Flame
    spread rate by fuel moisture content. Model ANOVA table in Table
    \ref{tab:spreadrate_anova} and coefficients in SI Table 4. E) Percent fuel
    consumed by moisture content. Lines indicate best fit beta regression
    lines. Model deviance table in Table \ref{tab:consume_anova} and
    coefficients are in SI Table 5. For plots in left column, horizontal jitter
    was added to avoid overplotting. for flammability plots, a lack of data at
    earlier time points for a taxon indicates no ignitions occurred at those
    time points.}
 \label{fig:drydown}
\end{figure}
%% \clearpage
